\documentclass[man,12pt,natbib]{apa6}
\usepackage[colorlinks=false]{hyperref}
\usepackage{amssymb,amsmath,times,CJKutf8}
\linespread{1.5}

\begin{document}

\title{Critique of \emph{The acquisition of communicative style in Japanese} by
	P. Clancy (1987)}
\shorttitle{Critique of Clancy (1987)}
\author{Edward Hern\'{a}ndez}
\date{4 December 2015}
\affiliation{College of William \& Mary}
\maketitle

% Each student will choose two of the articles assigned after Fall Break (other
% than an article that you presented in class) and provide a written critique
% (3pps.)   A critique includes a summary of the main argument of a text as
% well as discussion of an author’s use of particular terms or concepts, and a
% reasoned evaluation of the overall strength of their argument in light of
% other readings.  The first critiques is due within one week after the class
% in which the article was discussed.  The second critique is due on the last
% day of classes.  Please either submit critiques on paper or as an emailed
% Word attachment. 

\section{Summary}

\citet{Clancy87} claims that ``[t]he particular communicative style of a
culture arises from shared beliefs about people, what they are like, and how
they should relate to one another'' \cite[p.~245]{Clancy87}, and, further, that
this communicative style ``perpetuat[es] those beliefs \cite[p.~245]{Clancy87}.
From her data, she argues that in the case of Japanese children, this style is
acquired largely from the speech of the mother, and that, in this case, style
is often taught explicitly and intentionally.  She claims that it is largely
communicative style which is used to transmit ``cultural values to children''
\cite[p.~246]{Clancy87}.

\section{Terms}

Clancy relies on the idea of ``communicative style,'' as discussed by
\citet{Barlund75} (in another of Japanese speech) According to Clancy,
Barlund's definition ``[includes] the topics people discuss, their favorite
forms of interaction, the depth of involvement sought, the extent to which they
rely upon the same channels for conveying information, and the extent to which
they are tuned to the same level of meaning, such as factual versus emotional
competence'' \citep[p.~213]{Clancy87}.
Clancy also ``loosely'' defines the term as she uses it: ``the way language is
used and understood in a particular culture'' \citep[p.~213]{Clancy87}.

It seems to me that this is not as clear as it could (or should) be.  ``The way
language is used'' is, obviously, a topic worthy of linguistic study. However,
it is not clear to me that this is comprised of ``the way language is used and
understood'' is comprised of such disparate elements as ``the depth of
involvement sought'' and ``factual versus emotional competence.'' At least, I
don't think these aspects of language use are identifiable through (purely)
linguistic inquiry, even with an anthropological bent. Some of these questions
seem to me to require cognitive and (inter/ethno)cultural psychology in
addition to methods and theories in linguistics. To what extent is
conflict-avoidance an element of \emph{communicative} style? It is well
attested that avoiding conflict and maintaining face are culturally important
to the Japanese \citep{Benedict46,Ohbuchi94}. If a businessman avoids a
conversation altogether to avoid the conflict it might contain, is that part of
communicative \emph{style}? I find it hard to conceptualize the boundaries of
the concept as it is described here.

Clancy also claims that communicative style is ``obviously'' ``one aspect of
`communicative competence''\thinspace ' \citep[p.~213]{Clancy87}, which she
links to the idea of ``rules for use'' \citep{Hymes72}, which ``govern
speakers' production . . .  of language appropriately in context''
\citep[p.~213]{Clancy87}.  I am somewhat confused by this claim. I am not
entirely sure to what effect it is being employed. Is this just to say that
communicative style is socially consequential?  She similarly invokes the ideas
of social cognition, world view \citep{Whorf56}, and ``reality sets[s]''
\citep{Scollon81}, without making their use in her analysis particularly clear.

In the context of Japanese communicative style (and world view) she discusses
\emph{omoiyari} \begin{CJK}{UTF8}{min}(思いやり)\end{CJK} which she defines
simply as ``empathy'' \citep[p.~214]{Clancy87}. She holds that \emph{omoiyari}
is ``emphasize[d]'' by ``a set of cultural values'' which ``[set] the basis of
[the] style'' of Japanese communication \cite[pp.~213-214]{Clancy87}. She
identifies these values as dispreference for verbosity, indirection, conflict
avoidance, and unanimity \citep[p.~214-216]{Clancy87}.

This is less than ideal. \emph{Omoiyari} is not a particularly simple word (to
translate), as it carries a lot of cultural weight. ``Empathy'' is not an
\emph{incorrect} translation \citep{Travis98}, but it would be just as correct
to say sympathy, or compassion, or ``altruistic sympathy'' \citep{Hara06}.
While \emph{omoiyari} is indeed regarded as a central cultural value in Japan,
it is far from the only value, and it would be a mistake to attribute the whole
of the Japanese communicative style to it. In particular, I think it would be a
mistake to attribute conflict-avoidance to an expression of this trait. Other
studies have cited conceptions of interdependence or collectivism as a probable
cause for this behavior \citep{Ohbuchi94}, and I think it would be a mistake to
conflate those concepts with \emph{omoiyari} without a compelling reason.

\section{Evaluation}

I am concerned that this paper does not account for gender differences.
Japanese is spoken quite differently by male and female speakers. Particular
words are considered more masculine or more feminine than others, and there are
gendered sentence-final particles \citep{Siegal03}. However, these are not the
only differences. Men tend to more assertive (not omitting the copula
\emph{da}, using fewer polite forms, etc.), exhibit less exhibit fewer
instances of backchannel communication (\emph{aizuchi} forms;
\citealp{Kita07,Tanaka04}), and display a ``self-oriented'' speaking style
(contrary to Clancy's claims about \emph{omoiyari}; \citealp{Itakura04}).
Obviously, these traits all fall within the umbrella of communicative style.
How do the female participants look different from the male one? Did they in
this study? I think that data is of interest, and is certainly important to
report.

Additionally, I am uncomfortable with discussion of Japan as a homogeneous
society. Conformity is often discussed as a primary Japanese cultural value,
often foregrounding \emph{omoiyari} as central to Japanese uniformity. Clancy
says: ``the individual is seen primarily as a member of a social group, with a
responsibility to uphold the interests of that group. Thus arises the need for
empathy and conformity, which help to preserve group harmony and group
values.'' I am not so sure that Japanese conformity is a benevolent, empathetic
phenomenon.  Despite the strong national discourse of homogeneity, Japanese in
a multi-ethnic society with strong minority communities \citep{Lie01} This
discourse is mobilized against these minorities in racist, xenophobic ways
which serve to marginalize those who do not conform \citep{Diene06}. To take
this discourse at face value and accept the common attitude that it as rooted
in empathy is, I think, to disregard the social realities of Japan.


\clearpage

\title{Critique of \emph{Learning to listen: Confronting two meanings of
language loss in the contemporary White Mountain Apache speech community} by M.
E. Nevins (2004)}
\shorttitle{Critique of Nevins (2004)}
\author{Edward Hern\'{a}ndez}
\date{8 December 2015}
\affiliation{College of William \& Mary}
\maketitle

% Each student will choose two of the articles assigned after Fall Break (other
% than an article that you presented in class) and provide a written critique
% (3pps.)   A critique includes a summary of the main argument of a text as
% well as discussion of an author’s use of particular terms or concepts, and a
% reasoned evaluation of the overall strength of their argument in light of
% other readings.  The first critiques is due within one week after the class
% in which the article was discussed.  The second critique is due on the last
% day of classes.  Please either submit critiques on paper or as an emailed
% Word attachment. 

\section{Summary}

\citet{Nevins04} discusses ``language loss'' on the White Mountain Apache
Reservation. To outsiders, the Apache language appears relatively secure: ``the
everyday conversation of most older people, most adults in their thirties, and
probably about half of the people in their mid-twenties was conducted
frequently in Apache, sprinkled with English words or phrases''
\citep[p.~270]{Nevins04}. This is a far cry from many ``colonized speech
communities'' (p.~270), in which ``only a few elders speak the language
fluently'' (p.~270), but the White Mountain Apache still perceive the language
``to be in decline and threatened with replacement'' (p.~270) by English. This
perception consists \emph{not only} in a perceived decline in the use of the
language (among children), but also a perceived deterioration of traditional
Apache pedagogical relationships between elders and children.


\section{Terms}

As Nevins highlights in the title, ``language loss'' has many meanings. It
certainly means different things to linguists and speakers in colonized speech
communities.  To linguists it generally means something empirical. It might
consist in a decline in incidence of conversation in the language, or in the
number of fluent speakers. To speakers of the language, it might mean something
completely different, like the language no longer being used in a particular
setting, or a deterioration of particular social structures which are tied to
language ideologies. Nevins argues for listening to the definitions in the
community, rather than relying on our own.

Nevins uses the term ``language maintenance'' (pp.~269,~271,~274,~277,~284) or
simply ``maintenance'' (p.~272), to refer to efforts to address language loss.
This is a term used widely to refer to the actions of linguists in colonized
speech communities, and is used widely in the literature that Nevins cites in
this paper \citep{Fase92,LiebeHarkort79}.  If I remember correctly from my
conversations with Prof. Martin, this term is no longer in vogue, having been
largely supplanted by ``language revitalization'' (J. Martin, personal
communication, Spring 2015).  Nevins argues for a reconceptualization of
maintenance, which accounts for ``locally derived language ideologies, ways of
speaking, and pedagogical practices'' (p.~284).  I believe that it is this sort
of reconceptualization that motivated the change in terminology, from
``maintenance'' to ``revitalization.''

Nevins uses a term from \citet{Silverstein98}: ``social scientific
reflexivity'' (p.~408). It refers to the political relationships into which
linguists enter with the communities which they study. Nevins echoes
Silverstein's call ``to avoid---or at least to face---the ironies of being more
an agent of essentially colonial cultural change in local communities, the more
one merely desires to play a role in sustaining or fixing a local language
structure within the institutional assumptions of the surrounding society''
\citet[p.~408]{Silverstein98}. When we as ``experts,'' as part of a historical
pattern of colonial influences, enter a community to study their language, we
must be aware of the power we wield. Nevins asserts that this should not be
limited to internal critique. We should not simply reflect and be careful; we
should involve the community in decision making, and engage with local
discourses.


\section{Evaluation}

The work that this paper does is essential to the work of language maintenance.
It is an abuse of our positions as ``experts'' to perform language maintenance
without listening to the ideologies of the speech community for whom the
maintenance is being performed. With cultural pedagogies in mind, we as
linguists have to find a new role in language education which neither
underutilizes our expert knowledge of language nor invalidates the ideologies
or practices of the speakers. As this paper illustrates, this is not easy work,
but it is absolutely necessary if we wish to be effective in our language
maintenance efforts in colonized speech communities.

Nevins brings up another point which I think deserved more discussion than she
gave it: that teaching by translation is unreliable. According to one of the
Apache speakers cited in the paper, Mr. Cruz, the children are being taught
that ``\emph{nakih} means two'' (p.~283) in school. It is not clear to me
whether he means literally that \emph{nakih} means something other than `two,'
or whether this is merely a metaphor to illustrate a flawed practice. I think
it is worth considering that \emph{nakih} may mean something which is not
identical to `two.' I think it seems simplest to teach students who already
fluently speak a language numbers simply by translation: ``\emph{nakih} means
two.'' However, this runs a risk of teaching an understanding of words which 
does not line up with the understanding of fluent speakers (as Mr. Cruz notes,
these students will not think, as he does, of a vital presence moving in the
mountains when they think \emph{shash}). Numbers seem, perhaps, immune to this
sort of confusion, but number words are not universals. Speakers of Pirah\~{a},
for instance, may not have number words at all, and if they do, their use is
entirely unlike ours \citep{Gordon04,Frank08,Everett12}. The differences do not
have to be this pronounced to be important, either; in Koasati, the number
words are verbs, which effects the ways in which they are used (J. Martin,
personal communication, Spring 2015). If a speaker were merely taught that the
Koasati number word ``means two,'' they would not have a full understanding of
the meaning which current fluent speakers have.


\clearpage
\bibliography{course,extra}

\end{document}

\clearpage
\bibliography{course,extra}

\end{document}
