\documentclass[man,12pt,natbib]{apa6}
\usepackage[colorlinks=false]{hyperref}
\usepackage{amssymb,amsmath,times,CJKutf8}
\linespread{1.5}

\begin{document}

\title{Critique of \emph{Learning to listen: Confronting two meanings of
language loss in the contemporary White Mountain Apache speech community} by M.
E. Nevins (2004)}
\shorttitle{Critique of Nevins (2004)}
\author{Edward Hern\'{a}ndez}
\date{8 December 2015}
\affiliation{College of William \& Mary}
\maketitle

% Each student will choose two of the articles assigned after Fall Break (other
% than an article that you presented in class) and provide a written critique
% (3pps.)   A critique includes a summary of the main argument of a text as
% well as discussion of an author’s use of particular terms or concepts, and a
% reasoned evaluation of the overall strength of their argument in light of
% other readings.  The first critiques is due within one week after the class
% in which the article was discussed.  The second critique is due on the last
% day of classes.  Please either submit critiques on paper or as an emailed
% Word attachment. 

\section{Summary}

\citet{Nevins04} discusses ``language loss'' on the White Mountain Apache
Reservation. To outsiders, the Apache language appears relatively secure: ``the
everyday conversation of most older people, most adults in their thirties, and
probably about half of the people in their mid-twenties was conducted
frequently in Apache, sprinkled with English words or phrases''
\citep[p.~270]{Nevins04}. This is a far cry from many ``colonized speech
communities'' (p.~270), in which ``only a few elders speak the language
fluently'' (p.~270), but the White Mountain Apache still perceive the language
``to be in decline and threatened with replacement'' (p.~270) by English. This
perception consists \emph{not only} in a perceived decline in the use of the
language (among children), but also a perceived deterioration of traditional
Apache pedagogical relationships between elders and children.


\section{Terms}

As Nevins highlights in the title, ``language loss'' has many meanings. It
certainly means different things to linguists and speakers in colonized speech
communities.  To linguists it generally means something empirical. It might
consist in a decline in incidence of conversation in the language, or in the
number of fluent speakers. To speakers of the language, it might mean something
completely different, like the language no longer being used in a particular
setting, or a deterioration of particular social structures which are tied to
language ideologies. Nevins argues for listening to the definitions in the
community, rather than relying on our own.

Nevins uses the term ``language maintenance'' (pp.~269,~271,~274,~277,~284) or
simply ``maintenance'' (p.~272), to refer to efforts to address language loss.
This is a term used widely to refer to the actions of linguists in colonized
speech communities, and is used widely in the literature that Nevins cites in
this paper \citep{Fase92,LiebeHarkort79}.  If I remember correctly from my
conversations with Prof. Martin, this term is no longer in vogue, having been
largely supplanted by ``language revitalization'' (J. Martin, personal
communication, Spring 2015).  Nevins argues for a reconceptualization of
maintenance, which accounts for ``locally derived language ideologies, ways of
speaking, and pedagogical practices'' (p.~284).  I believe that it is this sort
of reconceptualization that motivated the change in terminology, from
``maintenance'' to ``revitalization.''

Nevins uses a term from \citet{Silverstein98}: ``social scientific
reflexivity'' (p.~408). It refers to the political relationships into which
linguists enter with the communities which they study. Nevins echoes
Silverstein's call ``to avoid---or at least to face---the ironies of being more
an agent of essentially colonial cultural change in local communities, the more
one merely desires to play a role in sustaining or fixing a local language
structure within the institutional assumptions of the surrounding society''
\citet[p.~408]{Silverstein98}. When we as ``experts,'' as part of a historical
pattern of colonial influences, enter a community to study their language, we
must be aware of the power we wield. Nevins asserts that this should not be
limited to internal critique. We should not simply reflect and be careful; we
should involve the community in decision making, and engage with local
discourses.


\section{Evaluation}

The work that this paper does is essential to the work of language maintenance.
It is an abuse of our positions as ``experts'' to perform language maintenance
without listening to the ideologies of the speech community for whom the
maintenance is being performed. With cultural pedagogies in mind, we as
linguists have to find a new role in language education which neither
underutilizes our expert knowledge of language nor invalidates the ideologies
or practices of the speakers. As this paper illustrates, this is not easy work,
but it is absolutely necessary if we wish to be effective in our language
maintenance efforts in colonized speech communities.

Nevins brings up another point which I think deserved more discussion than she
gave it: that teaching by translation is unreliable. According to one of the
Apache speakers cited in the paper, Mr. Cruz, the children are being taught
that ``\emph{nakih} means two'' (p.~283) in school. It is not clear to me
whether he means literally that \emph{nakih} means something other than `two,'
or whether this is merely a metaphor to illustrate a flawed practice. I think
it is worth considering that \emph{nakih} may mean something which is not
identical to `two.' I think it seems simplest to teach students who already
fluently speak a language numbers simply by translation: ``\emph{nakih} means
two.'' However, this runs a risk of teaching an understanding of words which 
does not line up with the understanding of fluent speakers (as Mr. Cruz notes,
these students will not think, as he does, of a vital presence moving in the
mountains when they think \emph{shash}). Numbers seem, perhaps, immune to this
sort of confusion, but number words are not universals. Speakers of Pirah\~{a},
for instance, may not have number words at all, and if they do, their use is
entirely unlike ours \citep{Gordon04,Frank08,Everett12}. The differences do not
have to be this pronounced to be important, either; in Koasati, the number
words are verbs, which effects the ways in which they are used (J. Martin,
personal communication, Spring 2015). If a speaker were merely taught that the
Koasati number word ``means two,'' they would not have a full understanding of
the meaning which current fluent speakers have.


\clearpage
\bibliography{course,extra}

\end{document}
