\documentclass[12pt]{article}
\usepackage{etoolbox,keyval,ifthen,url,csquotes}
\usepackage[notes,strict,backend=biber,autolang=other,%
bibencoding=inputenc]{biblatex-chicago}
\usepackage{setspace}

\addbibresource{midterm.bib}

\setlength{\oddsidemargin}{-0.25in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{7in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-.75in}  % Top margin of 2 in -0.75 in = 1 in
\setlength{\textheight}{9.2in}  % Lower margin of 11 in - 9 in - 1 in = 1 in
\linespread{1.5}

\renewcommand{\footnoterule}{%
  \kern -3pt
  \hrule width 3in height 1pt
  \kern 5pt
}

\begin{document}
\title{Shared Trauma and Healing in Toni Morrison's \emph{Home}}
\author{Edward Hern\'{a}ndez}
\date{\today}

\maketitle

\abstract{This paper traces the narrative arc of Toni Morrison's \emph{Home},
highlighting Frank and Cee's joint healing process and applying this process as
a framework under which to practice narrative medicine with respect to moral
injury.}

\vspace{12pt}

\section{Introduction}

Toni Morrison, in the novel \emph{Home}\autocite{Morrison12}, explores the
themes of shared suffering and shared healing. In the text, Frank Money, a
Korean War veteran, struggles with moral injury both from the war and from his
childhood. At the same time, he must rescue and care for his sister Cee, who is
physically ill, having been subjected to inhumane experimentation.  This paper
will examine this narrative arc and its implications for healing through the
narrative medicine lens provided by Rita Charon.\autocite[ch.~6]{Charon06}
Charon identifies five elements of a text to which a close reading ought to
attend: frame, form, time, plot, and desire. Each is critical to a full
appreciation of \emph{Home}., but for the sake of depth, I will focus on two in
this paper: form and desire.

\section{Form}

The form in which the narrative of \emph{Home} is told is striking. Even
assigning a genre to the text is tricky. As Leah Hager Cohen describes it, it
is ``on the basis of its publisher’s description a novel, on the basis of its
length a novella, and on the basis of its stripped-down, symbol-laden plot
something of an allegory.''\autocite{Cohen12} Beyond the genre confusion, the
text is odd in that it is quilted together of dissimilar pieces, told by two
narrators of different types, with wildly different styles. Some chapters
feature an omniscient narrator telling Frank and Cee's stories in the third
person with smooth, controlled prose. Others are told by Frank himself, in
short, jagged, halting, first-personal sentences. While Frank is not an
omniscient narrator, he speaks directly with the reader and the other narrator.
% Is the author/narrator really omniscient if the Frank narrator can dupe
% him/her and withold portions of the story? Why does this matter?

These stylistic choices serve to highlight Frank's complex relation to his own
story. It is his story in that it is about him. It is the story of his life, of
his childhood, his experience in the war, his journey to rescue his sister. But
no matter how personal it is, the story does not belong solely to him. It is
also Cee's story, of their shared childhood, of her rescue by Frank, of how his
experiences impact her. It is the story of the killed man, of his death, of the
children witnessing his burial, of his ritual re-burial. These stories cannot
be fully told without being told together.

In the same way that the story cannot be individual, Frank and Cee do not
suffer in isolation. Frank suffers in the same way as many veterans of combat.
His time on the battlefield in Korea damages his mind and his spirit. He
experiences what Rita Nakashima Brock calls ``moral injury,'' which she
describes as ``the collapse of your moral meaning system and your moral
foundations because of things that you've experienced.''\autocite{Brock15} He
killed a Korean girl during the war, knowing full well that the act was
horrible. This produced cognitive dissonance between his positive, righteous
self image, feeling ``so proud grieving over [his] dead friends'',\autocite[p.
133]{Morrison12} and the guilt and shame he felt for for his actions. While
Frank's suffering stems from very personal experiences, many veterans commit or
experience similar horrors, and subsequently have to deal with the same sort of
dissonance and injury. Frank's moral pathology is shared by many who fought
with him.

Similarly, Cee's encounter with the doctor is part of a larger pattern, of
exploitative research on Black bodies and on Black women's reproductive systems
specifically. White science and medicine have long been attracted to the study
of the Other. Throughout the 19th century, Khoikhoi women like Saartjie
Baartman were studied and exhibited while they were alive, and dissected after
they were dead, to discover the secrets of their physiological (especially
sexual) differences from the white body.\autocite{Qureshi04} As recently as
1972, the Public Health Service studied the effects of syphilis on black men's
reproductive systems without offering them any treatment or even notifying them
that they had the disease. Perhaps the most striking similarity to Cee's case
is the work of J. Marion Sims, considered ``the father of modern gynecology'',
whose work consisted primarily of exploratory surgery on enslaved black women
without anesthesia.\autocite{Spettel11} Cee, like Frank, suffers together with
others who have similar traumatic experiences.
% good
% excellent additional sources

The sharing of particular sorts of experiences is not the only way that the
sufferers of trauma are tied together, however. This is perhaps more visible in
the case of the killed man. Neither Frank nor Cee are killed with him, nor do
they see him killed. They do not interact with him while he is alive, nor do
they knowingly interact with his killers. Nonetheless, they are effected by his
death. Seeing him buried is a traumatic experience which haunts both of them
for years. Being in the same community as those who undergo trauma effects all
members of the community in some way, however small. Additionally, recent
research is beginning to show that this sort of trauma can be passed down, from
one generation to the next,\autocite{Dias14,Love10} meaning that our stories
are inseparable not only from everyone in our communities, but everyone who
came before us. This is why the text must be written from different
perspectives, including the omniscient.
% Good, but even omnicience is fallible and "imperfect" when systems of moral
% meaning break down

\section{Desire}

Frank, as a narrator, desires to admit his experiences. He struggles throughout
the novel to tell us the truth, and as the novel progresses, this produces in
the reader a growing desire to know the truth. In chapter
15,\autocite[p.~133]{Morrison12} he finally gives in, and tells us what he has
been withholding, that he killed the Korean girl. It is hard to say that this
realization gives the reader any ``pleasure,'' but it certainly releases much
of the pent-up anticipation, anxiety, and curiosity about Frank's wartime
experiences.  Reaching this realization with Frank as he reaches the resolve to
tell it satisfies both the narrator's and reader's desires at once. As
unpleasant as it is to read, it is a release, a satisfaction, and thus a
``pleasure of the text'' as Roland Barthes discusses them.\autocite[p.
124]{Charon06}
% can you cite the text to offer proof of Frank's desire
% through what artistic and/or aesthetic means does Morrison accomplish the
% establishment of this anxiety in the reader?

Likewise, Frank. as a character, wants closure for the killed man. After seeing
him buried, he is so traumatized that he either forgets the experience or
claims to (much like the story of shooting the girl).\autocite[p.
5-6]{Morrison12} I would argue that seeing the man unceremoniously buried
constituted a moral injury undermining Frank's moral beliefs about the value of
life. Whether or not he remembered, and whether or not the injury was moral, he
is haunted by the experience, and cannot make peace with it until years later,
when he is able to return to the burial site and give the man a proper, marked
grave. This resolution, propelled by the desire of Frank the character, is a
\emph{pleasure} to the reader as well. It is the happiest ending we can hope
for in a story of trauma: the characters who survive make peace with it and
begin to heal. This ritual heals not only Frank, whose desire propels it, but
Cee as well, who, as we see in the final scene, was also haunted by the killed
man. Hager Cohen points out that this realization, that Cee also sees the man,
``underscores the book's most powerful proposition: that there is no such thing
as individual pathology.''\autocite{Cohen12}
% Good
% this ritual helps complete Cee's healing (to the extent that she is healed).
% However, it is the women of the community who accomplish Cee's primary
% healing, and she must be separated from all men, even her brother, for the
% effect of healing to take hold.

Nakashima Brock briefly discusses this idea as well in an interview. She
describes the ways in which her father's wartime experience was a shared trauma
among her family, to whom he returned almost
unrecognizable.\autocite{Brock15} Since we as people and communities are
so intertwined, we inevitably share our trauma and our pathology. We share our
desire for healing just as narrator, character, and reader share the desire in
\emph{Home}. We must harness this connectedness, our shared desire, to heal as
communities, just as we are hurt as communities.

\section{Conclusion}

Moral injury is pernicious. It not only harms us deeply, but it harms those
around us, and largely, it harms us without us knowing. Since most of us have
little to no understanding of what it is to be morally injured, we have no
understanding of how to heal from these injuries. Some work is being done to
give a psychological account of moral injury, and suggest clinical practices
for its treatment,\autocite{Litz09} but the work is far from complete, and what
sparse recommendations there are for treatment rely on the presence of
``benevolent moral authority.''\autocite[\S 7.2]{Litz09} Treatment under this
model may include ``an imaginary conversation with another person who [the
patient has] great respect for and who can weigh in as a relevant and generous
moral authority.''\autocite[\S 7.2.5]{Litz09} This is typical of a psychology
which embraces controls and fails to incorporate and embrace the complexities
of spirits and communities. The researchers picture healing happening person by
person, by imagining a community. But can we believe that Frank would heal, if
he only \emph{imagined} telling the truth? We need instead of \emph{imagined}
conversations, \emph{actual} conversations, where all those effected can heal
together. Toni Morrison's \emph{Home} points us toward the answer: we desire to
tell the truth to each other, and to hear the truth from each other; and when
we do, healing can begin.

% Lettini and Brock (required, per rubric) \\
% Van Der Noot (Required)

% Edward, You have written an interesting paper that is on its way to being a
% very good paper, but you have not followed the rubric. Therefore, I am
% returning the paper to you without a grade to give you the opportunity to
% re-write it in such a way that it fulfills the requirements. Please have your
% revision in my box in the English Department office by 4:30 on October 30.
% Your additional sources are very good but you must also follow the rubric.
% Please feel free to extend the length of the paper if that needs to happen as
% well.  Best wishes, Prof. Braxton


% Some questions to be explored in a future draft or expansion, if you choose:

% Q. What complementary models might Lettini and Brock offer to supplement the
%    work of Litz and Stein? See if you can address this question in the
%    current revision.

% Q. What are the rituals of healing specific to Cee?
 
% Q. What rituals of healing might have been provided for the survivor of the
%    "men turned into dogs" fight? Who might the healers have been? What does 
%    the text suggest?

% Q. What is the relationship between the two narrators of the text; what is
%    essential about the nature of the dialogue between them for our 
%    understanding of the text (and the nature of Frank's invisible wounds)?

% Q. How is Frank's sense of guilt for his arousal by the Korean girl he kills
%    connected to his feelings of protectedness for his sister (And why must 
%    his lifelong protection of Cee be interrupted by the women healers in 
%    order for Cee to heal)?


\clearpage
\printbibliography
\end{document}
