\documentclass[doc,12pt]{apa6}
\usepackage[colorlinks=false]{hyperref}
\usepackage{amssymb,amsmath,times,graphicx,tipa,phonrule,gb4e}
\linespread{1.5}

\begin{document}

\title{Homework 5: Dravidian Languages}
\shorttitle{Homework 5}
\author{Edward Hern\'{a}ndez}
\date{23 February}
\affiliation{with Sora Edwards-Thro}
\maketitle

\section{Tamil}

I propose that {[}\textipa{p b B}{]}, {[}\textipa{t d D}{]}, and {[}\textipa{k
g G}{]} are, respectively, allophones of three phonemes.  For each phoneme,
which allophone is produced can be predicted by two rules, one specifying
behavior in the word-initial position and one specifying behavior following
nasal consonants.
\begin{exe}
	\ex \phonl{\textipa{B}}{p}{\#}
	\ex \phonl{\textipa{B}}{b}{nasal C}
	\ex \phonl{\textipa{D}}{t}{\#}
	\ex \phonl{\textipa{D}}{d}{nasal C}
	\ex \phonl{\textipa{G}}{k}{\#}
	\ex \phonl{\textipa{G}}{g}{nasal C}
\end{exe}
Following nasal consonants, the sounds become voiced stops. This most likely
results from the release of the closures made to produce the nasal airflow.
In word-initial positions, they become voiceless stops. I am less sure of
why this occurs, but I expect that it is easier to produce that way.

These three phonemes are not the only sounds behaving in this way in the data.
Both retroflex stops and post-alveolar affricates are also becoming voiced
after nasal consonants.
\begin{exe}
	\ex \phonl{\textrtailt}{\textrtaild}{nasal C}
	\ex \phonl{\texttslig}{\textdyoghlig}{nasal C}
\end{exe}

The nasal sounds all seem to be undergoing place assimilation. They all seem to
be produced in the place of the immediately proceeding consonant, if there is
one. I'm not sure how to write this out as a rule.

\section{Malayalam}

In the Malayalam data, vowel length is contrastive. There are three minimal
pairs based on vowel length: {[}\textipa{ciri}{]} and {[}\textipa{ci:ri}{]},
{[}\textipa{ke{\textrtailt}:u}{]} and {[}\textipa{ke:{\textrtailt}:u}{]}, and
{[}\textipa{ka{\textrtailt}i}{]} and {[}\textipa{ka{\textrtailt}i}{]}. Since
these pairs exist, long and short vowels constitute different phonemes in
Malayalam (rather than being allophones of the same phoneme), so there cannot
be a meaning-independent rule that predicts which of them will appear in which
environments. There are also minimal pairs which establish that at minimum,
{[}i{]}, {[}e{]}, and {[}a{]} are phonemically distinct from /u/. I suspect
that each of these vowels is its own phoneme, making the vowel inventory of
Malayalam somithing like {[}\textipa{i u e e: a a:}{]}. There is not enough
data on {[}\textipa{@}{]} to decide whether or not it is phonemically distinct
from other vowels.

\end{document}
