\documentclass{article}
\usepackage[utf8]{inputenc}

\title{NO MORE MISS AMERICA!}
\author{Robin Morgan}
\date{22 August, 1968}

\begin{document}
\maketitle

FOR IMMEDIATE RELEASE

On September 7th in Atlantic City, the Annual Miss America Pageant will again
crown ``your ideal.'' But this year, reality will liberate the contest
auction-block in the guise of ``genyooine'' de-plasticized, breathing women.
Women's Liberation Groups, black women, high-school and college women, women’s
peace groups, women's welfare and social-work groups, women's job-equality
groups, pro-birth control and pro-abortion groups---women of every political
persuasion- all are invited to join us in a day-long boardwalk-theater event,
starting at 1:00 p.m. on the Boardwalk in front of Atlantic City's Convention
Hall. We will protest the image of Miss America, an image that oppresses women
in every area in which it purports to represent us. There will be: Picket
Lines; Guerrilla Theater; Leafleting; Lobbying Visits to the contestants urging
our sisters to reject the Pageant Farce and join us; a huge Freedom Trash Can
(into which we will throw bras, girdles, curlers, false eyelashes, wigs, and
representative issues of Cosmopolitan, Ladies' Home Journal, Family Circle,
etc.---bring any such woman-garbage you have around the house); we will also
announce a Boycott of all those commercial products related to the Pageant, and
the day will end with a Women's Liberation rally at midnight when Miss America
is crowned on live television. Lots of other surprises are being planned (come
and add your own!) but we do not plan heavy disruptive tactics and so do not
expect a bad police scene. It should be a groovy day on the Boardwalk in the
sun with our sisters. In case of arrests, however, we plan to reject all male
authority and demand to be busted by policewomen only. (In Atlantic City, women
cops are not permitted to make arrests---dig that!)


Male chauvinist-reactionaries on this issue had best stay away, nor are male
liberals welcome in the demonstrations. But sympathetic men can donate money as
well as cars and drivers. \underline{We} \underline{need} \underline{cars} to
transport people to New Jersey and back.

Male reporters will be refused interviews. We reject patronizing reportage.
Only newswomen will be recognized. 

Anyone interested in further information, and anyone willing to help with
ideas, transportation, money, or anything, can write us at: P.O. Box 531, Peter
Stuyvesant Station, New York, N.Y. 1009, or telephone (212) 475-8775 between
7:30 and 10:00 p.m. weeknights.  Get a group of women together, come to the
Miss America Pageant on Saturday, September 7th, and raise your voice for
Women's Liberation.  We will reclaim ourselves for ourselves. On to Atlantic
City!

The Ten Points\\
We protest:

\begin{enumerate}
	\item \textit{The Degrading Mindless-Boob-Girlie Symbol.} The Pageant
		contestants epitomize the roles we are all forced to play as women. The
		parade down the runway blares the metaphor of the 4-H Club county fair,
		where the nervous animals are judged for teeth, fleece, etc., and where
		the best ``Specimen'' gets the blue ribbon. So are women in our society
		forced daily to compete for male approval, enslaved by ludicrous
		``beauty'' standards we ourselves are conditioned to take seriously.

	\item \textit{Racism with Roses.} Since its inception in 1921, the Pageant
		has not had one Black finalist, and this has not been for a lack of
		test-case contestants. There has never been a Puerto Rican, Alaskan,
		Hawaiian, or Mexican-American winner. Nor has there ever been a true
		Miss America---an American Indian.

	\item \textit{Miss America as Military Death Mascot.} The highlight of her
		reign each year is a cheerleader-tour of American troops abroad---last
		year she went to Vietnam to peptalk our husbands, fathers, sons and
		boyfriends into dying and killing with a better spirit. She personifies
		the ``unstained patriotic American womanhood our boys are fighting
		for.'' The Living Bra and the Dead Soldier. We refuse to be used as
		Mascots for Murder.

	\item \textit{The Consumer Con-Game.} Miss America is a walking commercial
		for the Pageant's sponsors. Wind her up and she plugs your product on
		promotion tours and TV---all in an ``honest, objective'' endorsement.
		What a shill.

	\item \textit{Competition Rigged and Unrigged.} We deplore the
		encouragement of an American myth that oppresses men as well as women:
		the win-or-you’re-worthless competitive disease. The ``beauty contest''
		creates only one winner to be ``used'' and forty-nine losers who are
		``useless.''

	\item \textit{The Woman as Pop Culture Obsolescent Theme.} Spindle,
		mutilate, and then discard tomorrow. What is so ignored as last year's
		Miss America? This only reflects the gospel of our Society, according
		to Saint Male: women must be young, juicy, malleable---hence age
		discrimination and the cult of youth. And we women are brainwashed into
		believing this ourselves!

	\item \textit{The Unbeatable Madonna-Whore Combination.} Miss America and
		Playboy's centerfold are sisters over the skin. To win approval, we
		must be both sexy and wholesome, delicate but able to cope, demure yet
		titillatingly bitchy. Deviation of any sort brings, we are told,
		disaster: ``You won't get a man!!''

	\item \textit{The Irrelevant Crown on the Throne of Mediocrity.} Miss
		America represents what women are supposed to be: inoffensive, bland,
		apolitical. If you are tall, short, over or under what weight The Man
		prescribes you should be, forget it. Personality, articulateness,
		intelligence, and commitment---unwise. Conformity is the key to the
		crown---and, by extension, to success in our Society.

	\item \textit{Miss America as Dream Equivalent To-?} In this reputedly
		democratic society, where every little boy supposedly can grow up to be
		President, what can every little girl hope to grow to be? Miss America.
		That's where it's at. Real power to control our own lives is restricted
		to men, while women get patronizing pseudo-power, an ermine clock and a
		bunch of flowers; men are judged by their actions, women by appearance.

	\item \textit{Miss America as Big Sister Watching You.} The pageant
		exercises Thought Control, attempts to sear the Image onto our minds,
		to further make women oppressed and men oppressors; to enslave us all
		the more in high-heeled, low-status roles; to inculcate false values in
		young girls; women as beasts of buying; to seduce us to our selves
		before our own oppression.
\end{enumerate}

NO MORE MISS AMERICA

\end{document}
