\documentclass[man,12pt,natbib]{apa6}
\usepackage{amssymb,amsmath,latexsym,times}
\linespread{1.5}

% Page length commands go here in the preamble
%\setlength{\oddsidemargin}{-0.25in} % Left margin of 1 in + 0 in = 1 in
%\setlength{\textwidth}{7in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
%\setlength{\topmargin}{-.75in}  % Top margin of 2 in -0.75 in = 1 in
%\setlength{\textheight}{9.2in}  % Lower margin of 11 in - 9 in - 1 in = 1 in
\renewcommand{\baselinestretch}{1.5} % 1.5 denotes double spacing. Changing itwill change the spacing
\setlength{\parindent}{0in}

\begin{document}
\title{Wittgenstein on Private Language}
\author{Edward Hern\'{a}ndez}
\date{\today}
\affiliation{College of William \& Mary}
\shorttitle{Wittgenstein on Private Language}

\maketitle

% \vspace{-20pt}
\begin{quote}
	Consider \S 270 and \S 271.  Imagine that you are the person who discovers
	that whenever you have a particular sensation (which you note in your diary
	by writing ``S'') a medical apparatus shows that your blood-pressure rises.
	So you can say when your blood-pressure is rising without having to use
	that or any other apparatus. Wittgenstein asks ``And what reason do we have
	for calling `S' the name of [your] sensation?''

	Of course ``S'' is the name of your sensation, right?  It's that (privately
	felt) sensation which you make ``S'' stand for in your diary---and whose
	occurrence is objectively indicated by the medical apparatus---isn't it?
	If your answer to these questions is `no', then aren't you left with the
	conclusion that a sensation word like ``S'' doesn't really stand for/mean
	your felt sensation?  That ``the pain in my stomach I'm feeling right now''
	doesn't really stand for the pain that I'm feeling in my stomach right now?
	What does it stand for then?  My groaning?  My bending over and holding my
	stomach?  What if I feel it but don't do those things?  Is its meaning
	different then?

	As McGinn points out, Wittgenstein's ``Private Language Argument'' has been
	characterized as advocating a form of behaviorism.  Indeed, in \S 281 an
	interlocutor asks ``But doesn't what you say come to this: that there is no
	pain, for example, without pain-behavior?''

	Is this a fair characterization of what Wittgenstein is doing (or saying)?
	% Locke: a word stands privately for an idea in the speaker’s mind.  
\end{quote}
\clearpage

Let us suppose that I consciously attend to all of my sensations, marking them
in my diary.
% “All”?  Good luck!
Let us also suppose that I keep track of my blood pressure constantly. After
some time, I might reasonably find that every time I have a particular
sensation (for which I might mark ``S'' in my diary) my blood pressure rises.
% i.e., a manometer or something like that signifies a rise.
After some amount of time, I will feel comfortable saying that my blood
pressure rises when I feel \textit{S},
% There is a need to be clear, at least in this essay, that when you refer to
% “my blood pressure”, you mean the reading given by the machine that measures
% my [your] blood pressure. 
%
% So, there are at least 3 things at play here: (A) your sensation (IF it is
% always the same sensation), (B) the pressure in your blood stream, (C) the
% reading on the manometer.  And, of course, there is also the mark you make:
% “S”.
even without checking my blood pressure in any way.

It seems (to me) obvious and natural that I am here using ``S'' as the name for
my sensation---the sensation which accompanies my increased blood pressure.
\citet{Wittgenstein53}, however, asks what my justification here is for calling
``S'' the name of a sensation (\S 270).
% TJT: read 270 and discuss.
% You are “comfortable” saying your blood pressure rises when you feel S… There
% is a consistent correspondence.
%
% But, between what?  S & B?  S & C?  S & A?
%
% Isn’t it S &C the relationship that you “find that every time I mark S “my
% blood pressure rises”, and isn’t this the one you become “comfortable with”?  
%
% If so, then what does/would it matter if the S & A relationship was not in
% fact consistent?  “Now it seems quite indifferent whether I’ve recognized the
% sensation correctly or not”.  As long as that S&C relationship remains
% constant, the S&A one can vary limitlessly, as “a mere ornament not connected
% with the mechanism at all”: “.. a wheel that can be turned though nothing
% else moves with it [and so it] is not part of the mechanism” 271
%
% What if every time an implanted neural stimulus sends N to your brain, you
% say “I’m now experiencing the meaning of the word ‘soporific’”?  (Locke would
% say something like, I am entertaining the idea SOPORIFIC.) Would it matter if
% you were “regularly making a mistake in identifying” that meaning/idea? 
As he often does, he provides a possible answer immediately following his
question: ``Perhaps the kind of way this sign is employed in this
language-game'' \cite[\S 270]{Wittgenstein53}.  This is a sort of answer which
seems unintuitive at first glance --- is having sensations a language-game?
\emph{Naming} sensations, at the very least, seems like it must be. Therefore,
it would seem I would have to answer Wittgenstein: I am justified in calling
``S'' the name of my sensation because it is employed in a particular kind of
way in the language-game of naming a sensation.

This answer at first seems thoroughly unsatisfying, especially with ``Private
Language'' in mind. Naming a sensation---insofar as it is a distinct
language-game---requires quite a lot of foreknowledge.  I might imagine that
naming a sensation is simply a matter of making up a sign, ``S,'' which I
record at future occurrences of the sensation. Wittgenstein complicates this in
several ways. First, he asserts that it is not sufficient to merely focus on
the sensation and record a sign. If that is all I do, all I have accomplished
is committing something about the previous instances to memory;
% To what extent have you even done that?  Or, what does it amount to?
I do not establish criteria for the sign's application in the future. This
means that I cannot apply the sign meaningfully in the future.
% And even if you do, they (like a rule) still need to be applied in particular
% instances. Who can check whether you have applied them correctly? As you
% intended? You?
In addition, to do all of this, I need to have an understanding of what it is
to name. Otherwise, the act of concentrating my attention on a sensation and
recording some sign in my diary while experiencing that sensation, the
``ceremony'' I have performed amounts to nothing. As he says, ``much must be
prepared in the language for the mere naming to make sense'' \cite[\S
257]{Wittgenstein53}.

With all this in mind, it seems less natural that ``S'' is, in fact, the name
of my sensation. However, it still seems tenable. Suppose that what I need
\emph{is} prepared in the language: I have foreknowledge
% Odd word to use here.  Doesn’t it mean ‘advance knowledge’, as in
% foreknowledge of the coming storm? Don’t you mean something more like being
% familiar with?
of some language-game wherein I name sensations by recording signs in a diary.
As \citet{McGinn97} puts it, I have used ``S'' in ``the distinctive grammar of
sensation words.'' Then the concern is setting up criteria for the application
of that sign in future instances.
% The problem is the same for present instances. 
%
% TJT: Discuss problem of inner criteria: 265 (consulting the table in our
% imagination), 270 (criterion of the sensation’s identity just the fact that
% we always write “S” every time!)
Here, I might be tempted to say that my blood pressure
% … as recorded by the apparatus (manometer).  That is, there is a need to be
% clear, at least in this essay, that when you refer to “my blood pressure”,
% you mean the reading given by the machine that measures my [your] blood
% pressure. 
will serve as a criterion. If, at some future time, my blood pressure rises
\emph{and} I report ``S,'' that is a valid report---I have named my sensation
successfully.
% Reporting and naming are two different things, no?  (Socrates didn’t think
% so.)  It looks like you mean that, since (1) the manometer reading
% criterially determines the accuracy/inaccuracy of your reporting (by writing
% down “S”) the occurrence of the sensation and (2) you wrote down “S” at a
% time when the manometer reading rose, therefore your report was
% accurate/valid.  But how does this relate to having “named” the sensation? 

This account leads me somewhere, philosophically, that I am not sure I am
comfortable.
% …comfortable with.
I am now tempted to say that ``S'' does not name my sensation (some internal
object) but rather the incidence of my blood pressure rising. At the very
least, I feel compelled to say that my use of ``S'' can only be meaningful if
an independent means of verification (like my blood pressure) is available to
prove my usage correct. If I follow this line of thinking I am similarly
tempted to say that ``pain'' refers not to some internal sensation but rather
to pain-behavior---groaning, crying, etc.---or, at least, cannot occur in its
absence, which is thoroughly at odds with my commonsense view of pain (and all
sensations). Obviously, this reads like fairly classic behaviorism (a criticism
to which Wittgenstein responds in \S 307).  It seems that pain is identified
via behavior and that ostensive definition of the word does, in fact, rely on
the exhibition of pain-behavior. Likewise, it seems intuitive that a genius
child who names pain herself will not be able to communicate its meaning
without pain-behavior.
% Nice example. And, naturally, she wouldn’t call it “pain”, if she is naming
% it herself.  So, if it had no associative behavior—other than her saying “X
% again!”—then what could it possibly communicate?  What does this actually
% mean, i.e., that it couldn’t communicate anything?  What does it contrast
% with?  (i.e, some situation where something is communicated?)   What does
% ‘communicate’ mean here?
This, as \citet{McGinn97} points
out, shows us that the act of private definition ``has no connection with our
ordinary criteria for mastery of the concept of pain.'' This leads us toward a
behaviorist account of language and of word-meaning, but, so far as I can tell,
cannot account for signs in ``private language'' to mean anything whatsoever. 

Seemingly to expound on this point, Wittgenstein invites us to imagine another
scenario, which \cite{McGinn97} claims is to show us that ``an allegedly
private act of identifying what is introspected as `the same again' ... plays
no role'' in the language-game of naming the sensation or identifying my rise
in blood-pressure. I do not fully understand what it is that Wittgenstein
intends me to imagine, nor what I am supposed to gather from having imagined
it. McGinn is of some help here, but not nearly enough.  Wittgenstein invites
us to imagine that ``I regularly identify [``S''] wrong'' \cite[\S
270]{Wittgenstein53}, and asserts that this mistake ``does not matter in the
least'' (\S 270). McGinn seems to take this situation to be one in which the
``private ceremony of identification'' of ``S'' no longer accords with my
``public practice'' of detecting a rise in blood pressure. I suppose, then,
that this would mean that I begin to detect my blood pressure rising without
introspecting and marking ``S'' in my diary. She asserts that this goes to show
that the meaning of ``S'' is derived from its use in some particular
language-game (though I do not know which one she means), rather than from its
connection with a rise in blood pressure. I confess that I do not understand
the implications here.

I fear that it may be beyond my ability to determine whether Wittgenstein
\emph{intends} to endorse a behaviorist view in these sections of the
\emph{Investigations}. Additionally, I have become hesitant to say that
Wittgenstein ever advocates any one view in particular.  Rather, as throughout
the \emph{Investigations}, he seems here to be reacting against (his)
temptation(s) to philosophize in particular ways. It may just be that the ways
in which he is inviting us to think about sensation \emph{look} behaviorist.
Those positions may not be his conclusions (if he has conclusions at all). This
is the view which \citet{McGinn97} seems to take, and I am inclined to agree.
% Not clear what you mean by this: He invites us to think about sensation in
% ways that look behaviorist but that this is not his own conclusion?  If that
% is what he is doing, then maybe they only look behaviorist but aren’t really? 

Even if Wittgenstein does not intend to advocate for a position or make clear
conclusions, there are still conclusions which it is reasonable to draw from
his comments. I think that Wittgenstein argues against our commonsense views
% What exactly is ‘our commonsense view’ (e.g., of sensation language)?  There
% are philosophical views, and there are the things we commonly say: where do
% commonsense views fit in?  Is it our commonsense view that the word ‘black’
% means the color of this typeface?  We say that, yes, (and we would react
% normatively to anyone who denied it). But is this a view (a belief, an
% opinion, a proposition) that we hold?  
%
% Analogously, wouldn’t we object to anyone (who had read too much philosophy
% or linguistics) who said that, when I talk about “this pain I’m having at the
% top of my stomach”, I’m not really meaning/referring (even ‘naming’, in an
% extended sense) this sensation of pain that I (and no one else) am having –
% and that what it really means is the kind of groaning I accompany my talking
% with?  If “commonsense view” refers to that common/normative way of talking
% about sensations, then, no, I don’t think he does argue against our
% commonsense views.  What he argues against is taking the justification for
% (and, thus, the interpretation of) that common way of talking about
% sensations ultimately to be grounded in the same practices by which we would
% evaluate the justification of “I have a penny in my pocket” or “Pluto has 3
% moons”.   But this is the way one is strongly tempted to go once one has
% started, as the Augustinian example is meant to show, with the assumption
% that ‘every word has a meaning … correlated with the word.  It is the object
% [e.g., sensation] for which the word stands.” (cf. 264: “Once you know what
% the word signifies, you understand it, you know its whole application.”)
%
% “If we construe the grammar of the expression of sensation on the model of
% ‘object and name’, the object drops out of consideration as irrelevant”
% (293).  This doesn’t mean, as it would to a behaviorist, that the sensation
% drops out of consideration as irrelevant to the grammar of our language-games
% about sensations (e.g., that the pain I feel in my stomach does not come into
% the common-sensible ways you and I might talk about it).  Behaviorism is the
% dead end to which, in psychological discourse, the object-and-name (money and
% the cow we buy with it) model leads.  Better not to head down this road at
% all.
on private language in these sections of the \emph{Investigations}. It seems to
me that he stands in opposition to (or at least intends to show us alternatives
to) a view on which signs in private language can correspond easily to
sensations, without the use of language-games which we use to refer to
sensations generally.
% The way this is phrased seems to suggest that the problem is with “correspond
% easily”, so that, if we do (more difficultly) take into account the language
% games we play with sensation words, then signs do correspond to sensations.
% Is this what you mean?
I also agree with McGinn that these arguments stand in opposition to
\citet{James90} and his claim that there can be some internal language of
psychology, divorced cleanly from objective reference or outside verification.
Insofar as we need language-games to name sensations, James' proposed language
is inoperable. I do not, however, take this to be a rejection on Wittgenstein's
part, of mental events or an embrace of behaviorism. I think in \S 307 he is
stating that he means to illuminate grammatical fictions \emph{as opposed to
mental ones}. This means, as McGinn puts it, that ``The distinction between
psychological states and behaviour, which the picture of `inner states' is
meant to capture, is, at bottom, a grammatical one.'' This does not necessarily
imply that we are to bound to embrace behaviorism (though I leave open the
possibility that it points toward behaviorism as a likely source for a
resolution of the problems he raises here), but rather that we ought examine
the language-games involved with sensation lest we be taken in by this
grammatical distinction to believe that these sets---the psychological and the
behavioral---are cleanly separable.

% “Imagine a person who could not remember what the word ‘pain’ meant — so that
% he constantly called different things by that name — but nevertheless used it
% in accordance with the usual symptoms and presuppositions of pain” – in
% short, he uses it as we all do.  Here I’d like to say: a wheel that can be
% turned though nothing else moves with it is not part of the mechanism.
% Sec. 271
%
% “Suppose that everyone had a box with something in it which we call a
% “beetle”.  No one can ever look into anyone else’s box, and everyone says he
% knows what a beetle is only by looking at his beetle.  — Here it would be
% quite possible for everyone to have something different in his box.  One
% might even imagine such a thing constantly changing. — But what if these
% people’s word “beetle” had a use nonetheless? — If so, it would not be the
% name of a thing.  The thing in the box doesn’t belong to the language-game at
% all; not even as a Something: for the box might be empty. — No, one can
% ‘divide through’ by the thing in the box; it cancels out, whatever it is.
%
% That is to say, if we construe the grammar of the expression of sensation on
% the model of ‘object and name’, the object drops out of consideration as
% irrelevant”.  Sec. 293.
%
%248. The sentence “Sensations are private” is comparable to “One plays
%patience by oneself”.
%
%249. Are we perhaps over-hasty in our assumption that the smile of a baby is
%not pretence?  -- And on what experience is our assumption based? (Lying is a
%language-game that needs to be learned like any other one.)
%
%250.  Why can’t a dog simulate pain? Is it too honest?
%
%251. What does it mean when we say “I can’t imagine the opposite of this” or
%“What would it be like if it were otherwise?” – For example, when someone has
%said that my mental images are private or that only I myself can know whether
%I am feeling pain; and so forth.  Of course, here “I can’t imagine the
%opposite” doesn’t mean: my powers of imagination are unequal to the task. We
%use these words to fend off something whose form produces the illusion of
%being an empirical proposition but which is really a grammatical one. ….
%Example: “Every rod has a length”.
%
%253. “Another person can’t have my pains.” – My pains – what pains are they?
%What counts as a criterion of identity here?  
%
%254.  What we are ‘tempted to say’ … is not philosophy, but it is its raw
%material … something for philosophical treatment.  …. (255) …like an illness.

\clearpage

\bibliography{wittgenstein}

\end{document}
